The challenge and promise of software citation for credit, identification, discovery, and reuse

### 2016-03-23 SC-challenge.tex
added some notes to address reviewer comments

\usepackage{color}

@@

Modern science and engineering depend on software.
We use citation to acknowledge traditional research results published in archival journals and conferences, but no such accepted standard exists to credit the considerable efforts that go into software.
One method to increase the amount of software developed, shared, and credited is to treat a software release as a publication. 
In addition, since research results, including data, now depend on the specific software used (e.g., version), proper citation---and the associated preservation---is necessary to ensure reproducibility.
\textbf{The main challenge of software citation is that we need a way to uniquely identify released\slash published software so that it can be cited by others who use it.}
We also need a process to curate and review software.

@@

@@

@@

@@

>>>>

\usepackage{color}
\usepackage{xcolor}

@@

Modern science and engineering depend on software.
We use citation to acknowledge traditional research results published in archival journals and conferences, but no such accepted standard exists to credit the considerable efforts that go into software.
One method to increase the amount of software developed, shared, and credited is to treat a software release as a publication.\knnote{Dan: can you support this statement with a citation?} 
In addition, since research results, including data, now depend on the specific software used (e.g., version), proper citation---and the associated preservation---is necessary to ensure reproducibility.
\textbf{The main challenge of software citation is that we need a way to uniquely identify released\slash published software so that it can be cited by others who use it.}
We also need a process to curate and review software.

\knnote{introduce connection to data quality\slash information quality here}
Data provenance requires, among other things, record of software used to generate or process that data~\cite{Wilson:2014aa}.

@@

\knnote{mention workshops on software citation; University of Manchester (? can't actually find that one). Additional references are good.}

@@

\knnote{be more specific about related work targeting challenges}

@@

\knnote{suggest ``few possible answers or clear path that might be followed''}

@@

\knnote{add discussion of when software should be cited; mention F11 principles}
Question of when software should be cited; although no clear answer, in order to ensure reproducibility of research results, software should be cited if used directly and important to the results.
In other words, if using different software could produce different data or results, then the software used should be cited.
